Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-02 paper/paper_new.tex
Started to write transition out of the Related Work section.

This limitation is magnified when trying get a handle on the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, and the biodiversity community advocated for data fitness standards \cite{chapman2020developing}. Even so, metadata properties used to record image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, and serves to justify a new initiative at Tulane University, where staff are manually capturing content for 22 metadata properties, to get a handle on the quality of digitized specimens drawn from the INHS collection and iDigBio. This current process is costly in terms of labor and time, and underscores the need to explore automatic metadata generation [*extraction].

@@

\subsection{Automatic Metadata Generation}
Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX. Some of this metadata may be useful in for selecting a machine learning sample. A researcher may desire images captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to reply on manually generated descriptive metadata, which itself is sparse.

@@

features from fish images that were distilled down to four, using Principal
Component Analysis, and derived a linear model

@@

In some instances it is necessary to computationally straighten the
fish in the images \cite{MuozBenavent2018EnhancedFB} before further
processing can be attempted.

@@

>>>>

This limitation is magnified when trying to assess the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}. Even so, metadata properties used to record image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, and serves to justify a new initiative at Tulane University, where staff are manually capturing content for 22 metadata properties, to characterize the quality of digitized specimens drawn from the INHS collection and iDigBio. This current process is costly in terms of labor and time, error-prone, and underscores the need to
explore automatic metadata generation methods.

@@

\subsection{Automatic Metadata Generation}
Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse.

@@

features from fish images and derived a linear model

@@

In some instances fish in the images need to be computationally straightened
before further processing can be attempted \cite{MuozBenavent2018EnhancedFB}.

@@

Our work stands apart from previous work in that we are
addressing a different need. Lack of metadata is impeding scientific studies.
Our focus and motivation are different.
Effectively doing the computational pre-processing
that will enable further downstream analyses.

We are applying a variety of machine learning, image processing and
image informatics techniques to extract critical properties from the
images.  The properties will allow follow-on studies to identify
the specific images needed for a particular analysis, ensuring that
the specimen images meet both scientific and technical requirements.
